The Birth of a Galaxy: Population III Metal Enrichment and Population II Stellar Populations

### 2010-10-13 ms.tex
Completed first draft of paper.

\title{The Birth of a Galaxy: Population III Progenitors and
  Metal-enriched Stellar Populations}

@@

\altaffiltext{1}{Department of Astrophysical Sciences, Princeton
  University, Peyton Hall, Ivy Lane, Princeton, NJ 08544}
\altaffiltext{2}{Hubble Fellow}
\altaffiltext{3}{Center for Astrophysics and Space Sciences,
  University of California at San Diego, La Jolla, CA 92093}
\altaffiltext{4}{Kavli Institute for Particle Astrophysics and
  Cosmology, Stanford University, Menlo Park, CA 94025}
%\altaffiltext{5}{Michigan State University}
\email{jwise@astro.princeton.edu}

@@

  Population III stars first form in dark matter halos with masses
  around $10^6 \Ms$.  By definition, they are metal-free, and their
  protostellar collapse is driven by molecular hydrogen cooling in the
  gas-phase, leading to a massive characteristic mass $\sim 100~\Ms$
  and suppressed fragmentation.  Population II stars with lower
  characteristic masses form when the star-forming gas reaches a
  critical metallicity of $10^{-6} - 10^{-3}~Z_\odot$, depending on
  whether dust cooling is important.  We present adaptive mesh
  refinement radiation hydrodynamics simulations that
  self-consistently follow the transition from Population III to II
  star formation.  We model stellar radiative feedback with adaptive
  ray tracing.  A top-heavy initial mass function for the Population
  III stars is considered, resulting in a plausible distribution of
  pair-instability supernovae and associated metal enrichment.
  \textbf{Add results.}

@@

The first (Pop III) stars are metal-free and have a large
characteristic mass and suppressed fragmentation in its protostellar
collapse \citep{Abel00, ABN02, Bromm02_P3, Yoshida03, OShea07a}.  A
fraction of these stars enrich the surrounding intergalactic medium
(IGM) when they go supernova, which can happen in stars $\lsim40~\Ms$
in Type II supernovae (SNe) or in stars roughly between 140 \Ms~and
260 \Ms~in pair-instability SNe \citep[PISNe;][]{2002ApJ...567..532H}.
The host halo and the neighboring halos are then enriched with this
ejecta.  There exists a critical metallicity that is $\sim 10^{-6}
Z_\odot$ if dust cooling is efficient \citep{Omukai05,
  Schneider06_Frag, clark08} and $\sim 10^{-3.5} Z_\odot$ otherwise
\citep{Bromm01, 2009ApJ...691..441S}, where the gas can cool rapidly,
lowering its Jeans mass.  An intermediate characteristic mass of
$\sim10~\Ms$ can be occur if the gas cooling is suppressed to the
cosmic microwave background (CMB) temperature \citep{Larson98,
  Tumlinson07_IMF, 2009ApJ...691..441S}.  The resulting Population II
star cluster will thus have a lower characteristic stellar mass than
its metal-free progenitors.  In the local universe, stars in the Milky
Way halo and dwarf spheroidal (dSph) galaxies may be connected to
these first stellar clusters.  In the halo of the Milky Way, the most
metal-poor stars have a metallicity floor of [Z/H] = --4
\citep{Beers05}, and in dwarf spheroidal (dSph) galaxies this floor is
a factor of 10 higher \citep{Tolstoy04, Helmi06}.  \textbf{Check for
  more recent references.}

@@

We use the adaptive mesh refinement (AMR) code
\enzo~\citep{BryanNorman1997, OShea2004} that employs our
implementation of adaptive ray tracing for radiation transport
\citep{Wise10}.  To resolve minihalos with at least 100 dark matter
(DM) particles and follow the formation of the first generation of
dwarf galaxies, we use a simulation box of 1 Mpc that has a resolution
of $256^3$.  This gives us a DM mass resolution of 1840 \Ms.  We
refine the grid on baryon overdensities of $3 \times 2^{-0.2l}$, where
$l$ is the AMR level, resulting in a super-Lagrangian behavior.  We
also refine on a DM overdensity of $3 \times 2^l$ and always resolve
the local Jeans length by at least 4 cells.  The latter criterion
avoids any artifical fragmentation during gaseous collapses
\citep{Truelove97}.  We initialize the simulation with \textsl{grafic}
\citep{Bertschinger01} at $z = 130$ and use the cosmological
parameters from the 7-year WMAP data \citep{WMAP7}: $\Omega_M =
0.266$, $\Omega_\Lambda = 0.734$, $\Omega_b = 0.0449$, $h = 0.71$,
$\sigma_8 = 0.81$, and $n = 0.963$ with the variables having their
usual definitions.  The size of the box limits the simulation to an
ending point of $z=7$.

We use a non-equilbrium chemistry solver with 9 species of hydrogen,
helium, and molecular hydrogen \citep{Abel97}.  We will follow-up this
study with one that considers radiative cooling from metal-enriched
gas, using rates that are calculated from CLOUDY \citep{CLOUDY} and
the method of \citet{2008MNRAS.385.1443S}.

@@

Simulations have shown that the characteristic mass of Pop III stars
$M_{\rm char} \sim 100~\Ms$.  They form in molecular clouds that
coexist with the dark matter halo center with limited fragmentation
occurring during their collapse; however \citet{2009Sci...325..601T}
has recently shown that Pop III binaries may form in a fraction of
such halos.

@@

\begin{figure*}
  \plotone{f3}
  \caption{\label{fig:projections} Density-weighted projections of gas
    density (top), temperature (middle), and metallicity (bottom) at
    $z=7$.  The left column shows the entire simulation volume, where
    the center and right columns focus on the intense and quiet halos,
    respectively.  The metallicity projections are a composite picture
    of metals originating from Pop III (red) and Pop II (blue) stars.}
\end{figure*}

@@

We illustrate the state of the simulation at $z=7$ in Figure
\ref{fig:projections} with density weighted projections of gas
density, temperature, and metallicity, showing the entire box and
focusing on the two halos of interest.  The quiet and intense halos
are located in the bottom center and bottom right of the full box,
respectively.

\subsection{Halo evolution}
\label{sec:halo}

@@

\begin{figure}
  \epsscale{1.15}
  \plotone{f2}
  \caption{\label{fig:Zevo} Average stellar metallicities and gas
    metallicities enriched by Pop II and Pop III SNe of the
    intense (top) and quiet (bottom) halos.}
  \epsscale{1}
\end{figure}

@@

Both halos star forming Pop II stars when $M = 10^7 \Ms$.  This is
consistent with the filtering mass $M_f$ of high-redshift halos when
it accretes mainly from a pre-heated IGM \citep{gnedin98, gnedin00,
  Wise08_Gal}.  The quiet halo forms $10^5 \Ms$ of stars by $z=9$.
This initial starburst photo-evaporates the majority of its molecular
clouds, in addition to heating and ionizing the surrounding IGM out to
a radius of 10--15 kpc at $z=9$.  These respectively reduce the
in-situ and external cold gas supply that could feed future star
formation.

The gas fractions of both halos are depleted from 0.15 to 0.08 by
outflowing shocks driven by ionization fronts in their initial
starbursts.  The quiet halo never recovers to the cosmic fraction
$\Omega_b/\Omega_M$ for the following reason.  The lack of major
mergers of halos above the filtering mass leads to a small gas
fraction, cold gas reservoir, and stellar mass at later times.  This
plays a large role in gas accretion because halos with $M < M_f$ will
be likely photo-evaporated, hosting diffuse warm gas reservoirs
instead of cold dense cores.  During this quienscent period, the halo
mainly accretes warm diffuse gas from the filaments and IGM.  In
contrast, the intense halo grows from major mergers of halos with $M >
M_f$.  The progenitor halos involved in the major mergers are able to
host molecular clouds and have, in general, higher gas fractions.
Between $z=10$ and $z=8$, the gas fraction increases from 0.07 to 0.12
until it rapidly jumps to 0.14 when a gas-rich major merger occurs.
The stellar mass accordingly increases with the ample supply of cold
gas during this period.  The gas fraction then decreases slightly by
0.01 when galactic outflows are generated from the starburst
associated with this major merger.

@@

At $z \sim 8$, the metallicity of the intense halo dramatically
self-enriches itself by a factor of 30 to $[\bar{Z}_2/H] = -1.5$
during a starburst.  Because this halo is located in a large-scale
overdensity, the ejecta falls back into the halo after reaching
distances up to 20 comoving kpc, in turn keeping the halo gas
metallicity high because the inflows are relatively metal-rich
themselves.  Interestingly the first few Pop II star clusters have
[Z/H] between --1 and --2 and dominate the average stellar metallicity
at $z > 8$.  We further detail the formation of these clusters in
\S\ref{sec:pop}.  After the $z=8$ starburst, the average stellar
metallicity follows the average gas metallicity within 0.1 dex.

@@

\textit{Quiet halo}.--- The most massive progenitor interestingly
never hosts a Pop III star.  Instead a nearby halo forms a Pop III
star, which (randomly) produces a PISNe at $z=15.6$.  The associated
blastwave overruns the most massive progenitor, and the dense core
survives this event and is enriched by this PISN, triggering the
transition to Pop II star formation.  Other progenitors host three Pop
III stars, forming at $z = 15.4, 14.2, 13.8$, with the latter
producing a PISN.  Metal enrichment from these two PISNe and latter
intrinsic Pop II SF quench all Pop III star formation in this halo.

@@

\begin{figure*}
  \plottwo{f4a}{f4b}
  \caption{\label{fig:pops} The scatter plots show the star formation
    history of the intense (left) and quiet (right) halos as a
    function of metallicity at $z=7$.  Each circle represents a star
    cluster, whose area is proportional to its mass.  The open circles
    in the upper right represent sizes of $10^3$, $10^4$, and $10^5$
    \Ms~star clusters.  The upper histogram collects the star formation
    history into 25 equal temporal bins.  The right histogram depicts
    the stellar metallicity distribution.}
\end{figure*}

@@

\textit{Quiet halo}.--- 
A nearby PISNe provides a metallicity floor of [Z/H] = --2.8 at which
metallicity the first Pop II stars form.  The stellar metallicity
evolution exhibits what is expected from a relatively isolated system
with the stellar feedback steadily enriching the ISM, resulting in a
correlation between stellar age and metallicity.  After $z=10$ the
metallicities plateau at [Z/H] = --2.1 for reasons discussed in
\S\ref{sec:halo}.  Around $z=7.5$, a 25:1 minor merger occurs, and the
gas inside the satellite halo is compressed, triggering metal-poor,
[Z/H] = --3.2, SF during its nearest approach.  This halo infalls
through a filament, where most of metal enrichment in the quiet halo
occurs in bi-polar flows perpendicular to the galaxy disk and
filament.  The filament and thus this satellite halo remains
relatively metal-poor.  The bi-polar outflows and metal-poor filaments
are seen in the metallicity projections in Figure
\ref{fig:projections}.

\textit{Intense halo}.---

\subsection{Environments for starbursts and quiescent star formation}

\li Present the environment for bursting and quiescent star formation
history

\section{Discussion and Summary}

@@

Support for this work was provided by NASA through Hubble Fellowship
grant \#120-6370 awarded by the Space Telescope Science Institute,
which is operated by the Association of Universities for Research in
Astronomy, Inc., for NASA, under contract NAS 5-26555.  Computational
resources were provided by NASA/NCCS award SMD-09-1439.  The majority
of the analysis and plots were done with \texttt{yt}
\citep{yt_full_paper}.

>>>>

\title{The Birth of a Galaxy: Population III Metal Enrichment and
  Population II Stellar Populations}

@@

\altaffiltext{1}{Department of Astrophysical Sciences, Princeton
  University, Peyton Hall, Ivy Lane, Princeton, NJ 08544}
\altaffiltext{2}{Hubble Fellow}
\altaffiltext{3}{Center for Astrophysics and Space Sciences,
  University of California at San Diego, La Jolla, CA 92093}
\altaffiltext{4}{Kavli Institute for Particle Astrophysics and
  Cosmology, Stanford University, Menlo Park, CA 94025}
\email{jwise@astro.princeton.edu}

@@

  Population III stars first form in dark matter halos with masses
  around $10^6 \Ms$.  By definition, they are metal-free, and their
  protostellar collapse is driven by molecular hydrogen cooling in the
  gas-phase, leading to a massive characteristic mass $\sim 100~\Ms$
  and suppressed fragmentation.  Population II stars with lower
  characteristic masses form when the star-forming gas reaches a
  critical metallicity of $10^{-6} - 10^{-3}~Z_\odot$, depending on
  whether dust cooling is important.  We present adaptive mesh
  refinement radiation hydrodynamics simulations that
  self-consistently follow the transition from Population III to II
  star formation.  We model stellar radiative feedback with adaptive
  ray tracing.  A top-heavy initial mass function for the Population
  III stars is considered, resulting in a plausible distribution of
  pair-instability supernovae and associated metal enrichment.  We
  find that the gas fraction recovers from 5 percent to nearly the
  cosmic fraction in halos with merger histories rich in halos above
  $10^7 \Ms$.  A single pair-instability supernova is sufficient to
  enrich the host halo to a metallicity floor of $10^{-3} Z_\odot$ and
  to transition to Population II star formation.  Neighboring halos
  are enriched to metallicities 10--100 times lower as the enriching
  blastwaves mainly bypass them.  Stellar metallicities trace gas
  metallicities within 0.2 dex.  We find that stellar metallicities do
  not necessarily trace stellar ages, as mergers of halos with
  established stellar populations can create superpositions of $t-Z$
  evolutionary tracks.  We see a bimodal metallicity distribution that
  is created after a starburst occurs when the halo can cool
  efficiently through atomic line cooling.

@@

The first (Pop III) stars are metal-free and have a large
characteristic mass and suppressed fragmentation in its protostellar
collapse \citep{Abel00, ABN02, Bromm02_P3, Yoshida03, OShea07a}.  A
fraction of these stars enrich the surrounding intergalactic medium
(IGM) when they go supernova, which can happen in stars $\lsim40~\Ms$
in Type II supernovae (SNe) or in stars roughly between 140 \Ms~and
260 \Ms~in pair-instability SNe \citep[PISNe;][]{2002ApJ...567..532H}.
The host halo and the neighboring halos are then enriched with this
ejecta.  There exists a critical metallicity that is $\sim 10^{-6}
Z_\odot$ if dust cooling is efficient \citep{Omukai05,
  Schneider06_Frag, clark08} and $\sim 10^{-3.5} Z_\odot$ otherwise
\citep{Bromm01, 2009ApJ...691..441S}, where the gas can cool rapidly,
lowering its Jeans mass.  An intermediate characteristic mass of
$\sim10~\Ms$ can be occur if the gas cooling is suppressed to the
cosmic microwave background (CMB) temperature \citep{Larson98,
  Tumlinson07_IMF, 2009ApJ...691..441S}.  The resulting Population II
star cluster will thus have a lower characteristic stellar mass than
its metal-free progenitors.  In the local universe, stars in the Milky
Way halo and dwarf spheroidal (dSph) galaxies may be connected to
these first stellar clusters.  In the halo of the Milky Way, the most
metal-poor stars have a metallicity floor of [Z/H] = --4
\citep{Beers05}.  In dwarf spheroidal (dSph) galaxies, this floor is a
factor of 10 higher \citep{Tolstoy04, Helmi06}, however several metal
poor stars with $-4 < [\mathrm{Z/H}] < -3$ have been recently
discovered in dSphs \citep{Tafelmeyer10, Frebel10_Obs}.

@@

We use the adaptive mesh refinement (AMR) code
\enzo~\citep{BryanNorman1997, OShea2004} that employs our
implementation of adaptive ray tracing for radiation transport
\citep{Wise10}.  We have modified \enzo~to use the HLLC Riemann solver
\citep{Toro94_HLLC} for additional stability in strong shocks.  To
resolve minihalos with at least 100 dark matter (DM) particles and
follow the formation of the first generation of dwarf galaxies, we use
a simulation box of 1 Mpc that has a resolution of $256^3$.  This
gives us a DM mass resolution of 1840 \Ms.  We refine the grid on
baryon overdensities of $3 \times 2^{-0.2l}$, where $l$ is the AMR
level, resulting in a super-Lagrangian behavior.  We also refine on a
DM overdensity of $3 \times 2^l$ and always resolve the local Jeans
length by at least 4 cells.  The latter criterion avoids any
artificial fragmentation during gaseous collapses \citep{Truelove97}.
We initialize the simulation with \textsl{grafic}
\citep{Bertschinger01} at $z = 130$ and use the cosmological
parameters from the 7-year WMAP data \citep{WMAP7}: $\Omega_M =
0.266$, $\Omega_\Lambda = 0.734$, $\Omega_b = 0.0449$, $h = 0.71$,
$\sigma_8 = 0.81$, and $n = 0.963$ with the variables having their
usual definitions.  The size of the box limits the simulation to an
ending point of $z=7$.

We use a non-equilibrium chemistry solver with 9 species of hydrogen,
helium, and molecular hydrogen \citep{Abel97}.  We will follow-up this
study with one that considers radiative cooling from metal-enriched
gas, using rates that are calculated from CLOUDY \citep{CLOUDY} and
the method of \citet{2008MNRAS.385.1443S}.

@@

Simulations have shown that the characteristic mass of Pop III stars
$M_{\rm char} \sim 100~\Ms$.  They form in molecular clouds that
coexist with the dark matter halo center with limited fragmentation
occurring during their collapse; however \citet{2009Sci...325..601T}
and \citet{Stacy10_Binary} have recently shown that Pop III binaries
may form in a fraction of such halos.

@@

\begin{figure*}
  \epsscale{0.8}
  \plotone{f3}
  \epsscale{1}
  \caption{\label{fig:projections} Density-weighted projections of gas
    density (top), temperature (middle), and metallicity (bottom) at
    $z=7$.  The left column shows the entire simulation volume, where
    the center and right columns focus on the intense and quiet halos,
    respectively.  The metallicity projections are a composite picture
    of metals originating from Pop III (red) and Pop II (blue) stars.}
\end{figure*}

@@

We illustrate the state of the simulation at $z=7$ in Figure
\ref{fig:projections} with density weighted projections of gas
density, temperature, and metallicity, showing the entire box and
focusing on the two halos of interest.  The quiet and intense halos
are located in the bottom center and bottom right of the full box,
respectively.  Radiative and mechanical feedback create a multi-phase
medium inside these halos, which are embedded in a warm and ionized
IGM.

\subsection{Mass evolution}
\label{sec:halo}

@@

@@

Both halos star forming Pop II stars when $M = 10^7 \Ms$.  This is
consistent with the filtering mass $M_f$ of high-redshift halos when
it accretes mainly from a pre-heated IGM \citep{gnedin98, gnedin00,
  Wise08_Gal}.  Afterwards these halos can cool efficiently through
molecular and atomic hydrogen cooling, sustaining constant and
sometimes bursty star formation.  The latter characteristic is equated
with the definition of a galaxy.  The quiet halo forms $10^5 \Ms$ of
stars by $z=9$.  This initial starburst photo-evaporates the majority
of its molecular clouds, in addition to heating and ionizing the
surrounding IGM out to a radius of 10--15 kpc at $z=9$.  These
respectively reduce the in-situ and external cold gas supply that
could feed future star formation.

The gas fractions of both halos are depleted from 0.15 to 0.08 by
outflowing shocks driven by ionization fronts in their initial
starbursts.  The quiet halo never recovers to the cosmic fraction
$\Omega_b/\Omega_M$ for the following reason.  The lack of major
mergers of halos above the filtering mass leads to a small gas
fraction, cold gas reservoir, and stellar mass at later times.  This
plays a large role in gas accretion because halos with $M < M_f$ will
be likely photo-evaporated, hosting diffuse warm gas reservoirs
instead of cold dense cores.  During this quiescent period, the halo
mainly accretes warm diffuse gas from the filaments and IGM.  In
contrast, the intense halo grows from major mergers of halos with $M >
M_f$.  The progenitor halos involved in the major mergers are able to
host molecular clouds and have, in general, higher gas fractions.
Between $z=10$ and $z=8$, the gas fraction increases from 0.07 to 0.12
until it rapidly jumps to 0.14 when a gas-rich major merger occurs.
The stellar mass accordingly increases with the ample supply of cold
gas during this period.  The gas fraction then decreases slightly by
0.01 when galactic outflows are generated from the starburst
associated with this major merger.

\subsection{Metallicity evolution}

\label{sec:Zevo}
\begin{figure}
  \epsscale{1.15}
  \plotone{f2}
  \caption{\label{fig:Zevo} Mass-weighted stellar metallicities and
    gas metallicities enriched by Pop II and Pop III SNe of the
    intense (top) and quiet (bottom) halos.}
  \epsscale{1}
\end{figure}

@@

At $z \sim 8$, the metallicity of the intense halo dramatically
self-enriches itself by a factor of 30 to $[\bar{Z}_2/H] = -1.5$
during a starburst.  Because this halo is located in a large-scale
overdensity, the ejecta falls back into the halo after reaching
distances up to 20 comoving kpc, in turn keeping the halo gas
metallicity high because the inflows are relatively metal-rich
themselves.  The first few Pop II star clusters have [Z/H] between --1
and --2 and dominate the average stellar metallicity at $z > 8$.
After the $z \sim 8$ starburst, the average stellar metallicity
follows the average gas metallicity within 0.1 dex.

@@

\textit{Quiet halo}.--- The most massive progenitor interestingly
never hosts a Pop III star.  Instead a nearby halo forms a Pop III
star, which (randomly) produces a PISNe at $z=16$.  The blastwave
overruns the most massive progenitor, and the dense core survives this
event and is enriched by this PISN, triggering the transition to Pop
II star formation.  Other progenitors host three Pop III stars,
forming at $z = 15.4, 14.2, 13.8$, with the latter producing a PISN.
Metal enrichment from these two PISNe and Pop II SF quench Pop III
star formation in this halo.

@@

\begin{figure*}
  \plottwo{f4a}{f4b}
  \caption{\label{fig:pops} The scatter plots show the star formation
    history of the quiet (left) and intense (right) halos as a
    function of metallicity at $z=7$.  Each circle represents a star
    cluster, whose area is proportional to its mass.  The open circles
    in the upper right represent sizes of $10^3$, $10^4$, and $10^5$
    \Ms~star clusters.  The dashed lines in the right panel guide the
    eye to two stellar populations that were formed in two satellite
    halos, merging at $z=7.5$.  The upper histogram collects the star
    formation history into 25 equal temporal bins.  The right
    histogram depicts the stellar metallicity distribution.}
\end{figure*}

@@

\textit{Quiet halo}.--- A nearby PISNe provides a metallicity floor of
[Z/H] = --2.8 at which metallicity the first Pop II stars form.  The
stellar metallicity evolution exhibits what is expected from a
relatively isolated system with the stellar feedback steadily
enriching the ISM, resulting in a correlation between stellar age and
metallicity.  After $z=10$ the metallicities plateau at [Z/H] = --2.1
for reasons discussed in \S\ref{sec:halo}.  The SFR peaks at $z=10$
and decreases as the cold gas reservoir is depleted.  Around $z=7.5$,
a 25:1 minor merger occurs, and the gas inside the satellite halo is
compressed, triggering metal-poor, [Z/H] = --3.2, SF during its
nearest approach.  This halo infalls through a filament, where most of
metal enrichment in the quiet halo occurs in bi-polar flows
perpendicular to the galaxy disk and filament.  The filament and thus
this satellite halo remains relatively metal-poor.  The bi-polar
outflows and metal-poor filaments are seen in the metallicity
projections in Figure \ref{fig:projections}.  Stars with [Z/H] $<$ --3
compose 1.6 percent of the total stellar mass.

\textit{Intense halo}.--- In contrast with the quiet halo, the intense
halo undergoes a few major mergers of halos with an established
stellar population.  This creates a superposition of age-metallicity
tracks in the SFH, seen in the complexity of Figure \ref{fig:pops}.
The first two Pop II stellar clusters have an unusually high
metallicity [Z/H] $\sim$ --1, which occurs when a PISN blastwave
trigger star formation in two neighboring halos.  Most of the early
star formation occurs around [Z/H] = --2.5.  At $z=9$, the halo's
virial temperature reaches \tento{4} K.  This combined with a 10:1
merger creates a starburst that quickly enriches the halo to [Z/H] =
--1.5 by $z=8$.  The halo continues to enrich itself with further SF
until $z=7$.  The spikes in the scatter plot correspond to SN
triggered star formation in nearby molecular clouds that are enriched
up to a factor of 10 with respect to the ISM.  However the mass
fraction of these metal-rich, SN triggered clusters are small compared
to the total stellar mass.  The starburst at $z=9$ creates a bimodal
metallicity distribution with peaks at [Z/H] = --2.4 and --1.2 with
the metal-rich component mainly being created after the starburst.
Two systems with sizable stellar components merge into the halo at $z
\sim 8$, and their stellar populations are still discernible in the
metallicity-age plot, whose tracks are noted by dashed lines.  Stars
with [Z/H] $<$ --3 compose 1.8 percent of the total stellar mass.

\section{Discussion and Conclusions}

In this paper, we focus on the birth of two galaxies prior to
reionization with a cosmological AMR radiation hydrodynamics
simulation.  Supernovae from Pop III stars provide the necessary heavy
elements for the transition to a Population II stellar population,
which we have directly simulated.  These two galaxies have a 10--15\%
probability in surviving as present-day ``fossil'' galaxies
\citep{Gnedin06}, otherwise they will be incorporated into galactic
stellar halos.

We find that one PISN is sufficient to enrich the star-forming halo
and surrounding $\sim 5$ kpc to a metallicity of 10$^{-3} Z_\odot$,
given a Pop III characteristic mass of 100~\Ms.  If the first stars
have a lower characteristic mass that favor hypernovae
\citep{Tumlinson07_IMF}, then this metallicity floor should be lowered
by a factor of $\sim 10$ because (1) the metal ejecta is lowered by a
factor of $\sim 50$ and the mixing mass is decreased by a factor of
$(E_{\rm hyp}/E_{\rm PISN})^{3/5}$ in the Sedov-Taylor solution, where
$(E_{\rm hyp}/E_{\rm PISN}) \sim 0.1$ is the ratio of explosion
energies of a hypernova and PISN.  In the case where this metallicity
floor is less than the critical metallicity, then the next starburst
will further enrich the ISM, solidifying the transition to Pop II star
formation.  We conclude that it only takes one, at most two, SNe from
Pop III stars in the halo progenitors to complete the transition to
Population II \citep[see also][]{Frebel10}.  The question of whether
the critical metallicity is \tento{-6} or \tento{-3.5} $Z_\odot$ is
most applicable to nearby halos where the heavy elements mix slowly
into dense cores as the blastwave overtakes it.  Less than two percent
of stars have [Z/H] $< -3$ in both systems, consistent with
observations of metal-poor stars in the halo and dSphs
\citep[e.g.][]{Beers05, Frebel10_Obs}.

We also find that the merger history plays an important role in
supplying gas into halos after its first epoch of star formation,
mergers of halos below the filtering mass are inefficient in providing
gas whereas the opposite is true for merging halos above the filtering
mass.  Halos do not necessarily need $\tvir \ge 10^4$ K to form
significant stellar populations; however SFRs dramatically increase,
and thus metal enrichment, when this threshold is reached.  Halos with
mostly gas-poor mergers or a quiet merger history result in a
monotonic increase in metallicity with time.  Star formation histories
become more complex with multiple metallicity-age tracks if the halo
experiences mergers with other halos that have an established stellar
population.  Furthermore star formation that is triggered by
blastwaves interacting with molecular clouds can have metallicities up
to a factor of 10 higher than the main starburst.  Lastly we find that
a starburst at $\tvir = 10^4$ K enriches the host halo enough to
create a bimodal metallicity distribution, where the metal-poor
component is created before the burst.  Note that mergers of stellar
populations can also create a similar bimodal distribution.  Such
distributions are observed in dSphs \citep[e.g.][]{Battaglia10}.

We have shown that it is possible to simulate the formation of a
high-redshift dwarf galaxy and its entire star formation history,
which provides invaluable insight on the first galaxies and the role
of metal-free stars in the early universe.  There exists a wealth of
information in this simulation, and we plan to follow up this
preliminary report with more detailed analysis of the metal enrichment
of the IGM, global star formation rates, and observational connections
with high-redshift galaxies and Local Group dwarf galaxies in the near
future.

@@

Support for this work was provided by NASA through Hubble Fellowship
grant \#120-6370 awarded by the Space Telescope Science Institute,
which is operated by the Association of Universities for Research in
Astronomy, Inc., for NASA, under contract NAS 5-26555.  Computational
resources were provided by NASA/NCCS award SMD-09-1439.
J.~H.~W. thanks Renyue Cen, Amina Helmi, Marco Spaans, and Eline
Tolstoy for enlightening discussions.  The majority of the analysis
and plots were done with \texttt{yt} \citep{yt_full_paper}.
